\Huge \textcolor{titleTextColor}{ \textsf{ \fontsize{130}{100}\selectfont \textbf{GRASS}\,{\firalight GIS}: A General-purpose Geospatial Research Tool } }

### 2018-11-30 grassposter/2018_AGU_Geospatial_Research_Tool/poster.tex
poster: short points to fit the paper
git-svn-id: https://svn.osgeo.org/grass/grass-promo@73727 15284696-431f-4ddb-bdfa-cd5b030d7da7

\begin{itemize}
% Basic Topics
 \item Community-driven project
 \item Long-term releases, stable APIs and emphasis on science
 \item Single integrated environment for 2D and 3D raster analysis, image processing, vector data analysis and spatio-temporal data processing
% GRASS GIS
% distribution strives to provide single integrated environment for 2D and 3D
% raster analysis, image processing, vector data analysis and spatio-temporal
% data processing. It supports large raster files (billions of cells), vector
% topology, coupling with databases and 64 bit memory.
%  \item To support the needs of scientists, the documentation includes not only links to the source code, its history and
% its authors, but also links to research papers that describe the algorithms
% implemented in the modules.
\end{itemize}

@@

\begin{itemize}
 \item New code typically contributed to Addons repository.
 \item Mature code is moved to the main code base.
 \item Both main code base and Addons maintained by the community.
\end{itemize}

@@

\begin{itemize}
 \item Radim Blazek introduced several modules for vector network analysis in 2003
       including shortest path analysis (\gmodule{v.net.path}) and traveling salesman (\gmodule{v.net.salesman}).
 \item The number of available modules increased to almost 20.
 \item Stepan Turek implemented turns support into all relevant vector network modules in 2014.
%  \item Since version 7.0 fine control over node costs available.
% combination with r.cost/r.walk workflows \citep{Petrasova2014}
\end{itemize}

@@

\centering
\begin{minipage}{0.9\linewidth}
\begin{center}
\includegraphics[width=\textwidth]{network_trips}
A series of trips to collect samples across North Carolina, USA
for water quality measurements
as part of the Polyfluorinated Alkyl Substance Testing (PFAST) project.
Trips are distinguished by color and were computed using multiple
iterations of traveling salesman (\gmodule{v.net.salesman}).
\end{center}
\end{minipage}

@@

\vspace*{1.5cm}

\begin{minipage}{\linewidth}
\centering
\includegraphics[width=.7\linewidth]{images/temporal_precip_temp}
\\
Creating a synchronized animation of monthly total precipitation and mean temperature for NC, USA
\end{minipage}

\vspace*{1cm}

@@

\begin{itemize}
 \item \gmodule{r.sim.water} module \citep{Mitas1998b}
       for simulating overland flow integrated into the Emergency Routing Decision Planning \citep{raghavan2014deploying}.
% TODO: paralelized
 \item \gmodule{r.watershed} for least cost path water accumulation from 1989
       and updated for massive data sets in 2011.
% TODO: refs
 \item \cite{Petrasova2014} utilized in \emph{Tangible Landscape}, a tangible GIS system,
       \gmodule{r.damflood}, a dam break inundation simulation by \cite{cannata2012two}.
\end{itemize}

@@

\begin{minipage}{0.485\linewidth}
\centering
\includegraphics[width=0.7\textwidth]{rsimwater_architects}
\end{minipage}
~
\begin{minipage}{0.485\linewidth}
\includegraphics[width=\textwidth]{damflood_tangible}
\end{minipage}
\vspace{2mm}
\begin{center}
Overland flow simulated used for landscape
architecture design in Tangible Landscape environment (left)
and a dam breach on Lake Raleigh, NC, USA (right)
\end{center}

>>>>

\begin{itemize}
% Basic Topics
 \item Community-driven project
 \item Long-term releases, stable APIs and emphasis on science
 \item Single environment for vector data analysis, 2D and 3D raster analysis, image processing and spatio-temporal data
% GRASS GIS
% distribution strives to provide single integrated environment for 2D and 3D
% raster analysis, image processing, vector data analysis and spatio-temporal
% data processing. It supports large raster files (billions of cells), vector
% topology, coupling with databases and 64 bit memory.
%  \item To support the needs of scientists, the documentation includes not only links to the source code, its history and
% its authors, but also links to research papers that describe the algorithms
% implemented in the modules.
\end{itemize}

@@

\begin{itemize}
 \item New code typically contributed to Addons repository.
 \item Mature code is moved to the main code base.
 \item Organization into modules makes contributions easy.
 %  \item Both main code base and Addons maintained by the community.
\end{itemize}

@@

\begin{itemize}
 \item Several modules for vector network analysis by Radim Blazek available since 2003 (e.g. \gmodule{v.net.salesman}).
 \item The number of modules increased to almost 20.
 \item Turn support added by Stepan Turek in 2014.
%  \item Since version 7.0 fine control over node costs available.
% combination with r.cost/r.walk workflows \citep{Petrasova2014}
\end{itemize}

@@

\centering
\begin{minipage}{0.9\linewidth}
\begin{center}
\includegraphics[width=\textwidth]{network_trips}
Trips to collect samples across North Carolina, USA
as part of a water pollution testing project (PFAST).
% Polyfluorinated Alkyl Substance Testing
% Trips are distinguished by color and were computed using multiple
% iterations of traveling salesman (\gmodule{v.net.salesman}).
\end{center}
\end{minipage}

@@

\vspace*{.5ex}

\begin{minipage}{\linewidth}
\centering
\includegraphics[width=\linewidth]{images/temporal_precip_temp}
\\
Creating a synchronized animation of monthly total precipitation and mean temperature for NC, USA
\end{minipage}

% \vspace*{1cm}

@@

\begin{itemize}
 \item \gmodule{r.sim.water} \citep{Mitas1998b}
       overland flow simulation used for emergency routing \citep{raghavan2014deploying}.
% TODO: paralelized
 \item Least cost flow \gmodule{r.watershed} from '89
       updated for massive data in '11.
% TODO: refs
 \item \cite{Petrasova2014} used in \emph{Tangible Landscape}
       dam break inundation \gmodule{r.damflood} \cite{cannata2012two}.
\end{itemize}

@@

\begin{minipage}{0.47\linewidth}
\centering
\includegraphics[width=0.7\textwidth]{rsimwater_architects}
\end{minipage}
~
\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth]{damflood_tangible}
\end{minipage}
\vspace{0.1ex}
\begin{center}
Flow used for landscape
architecture design (left)
and a dam breach on Lake Raleigh, NC, USA (right)
\end{center}
